Designing Equitable Electricity Systems

### 2024-10-18 Slides_5_3_2024.tex

\begin{frame}{Background on Least-Cost Electricity Planning Models}
\begin{center}
\begin{tikzpicture}[node distance=2cm]
\node (start) [start, text width=5cm] {\shortstack[l]{• Electricity Demand \\ • Costs of New Generation \\ • Generation Characteristics\\
• Constraints}};

@@

\node (result) [stop, below of=obj] {\shortstack[l]{• Time-varying generation for each resource \\ • New Generation Capacity \\ • New Transmission Capacity}};

@@

\node (start) [start, text width=5cm] {\shortstack[l]{• Electricity Demand \\ • Costs of New Generation \\ • Generation Characteristics\\
• Constraints}};

@@

\node(obj2)[process, below of=obj, text width=8cm, xshift=0cm]{\shortstack[l]{$\min \max\{\text{PollutionExp}_1,...,\text{PollutionExp}_N\}$ \\ \textit{ 
   s.t.   }\text{Everyone gets electricity and nothing breaks,} \\
    $\text{      }\sum \text{Costs}<= C^*+Threshold$ }};

\node (result) [stop, below of=obj2] {\shortstack[l]{• Time-varying generation for each resource \\ • New Generation Capacity \\ • New Transmission Capacity}};

@@

@@

\begin{frame}{Our Approach}
    \begin{enumerate}
        \item Use EPA emissions data to calculate emissions rates (Pounds per MWh)
        \item Use InMap Source-Receptor Matrix to calculate how one MWh of generation for each resource affects population-weighted average exposure for different groups.
        \item Use Switch to calculate least cost planning costs.
        \item Modify and run switch to minimize air pollution exposure subject to a cost constraint.
    \end{enumerate}

@@

    Please feel free to contact me at:
    \href{mailto:lbeatty@edf.org}{lbeatty@edf.org}\\
    \vspace{1cm}

\begin{frame}{Bonus Slides}

>>>>

\begin{frame}{Background on Least-Cost Electricity Planning Models}
\begin{center}
\begin{tikzpicture}[node distance=2cm]
\node (start) [start, text width=5cm] {\shortstack[l]{Inputs\\• Electricity Demand \\ • Costs of New Generation \\ • Generation Characteristics\\
• Constraints}};

@@

\node (result) [stop, below of=obj] {\shortstack[l]{Outputs\\• Time-varying generation for each resource \\ • New Generation Capacity \\ • New Transmission Capacity}};

@@

\node (start) [start, text width=5cm] {\shortstack[l]{Inputs\\• Electricity Demand \\ • Costs of New Generation \\ • Generation Characteristics\\
• Constraints}};

@@

\node(obj2)[process, below of=obj, text width=8cm, xshift=0cm]{\shortstack[l]{$\min \max\{\text{PollutionExp}_1,...,\text{PollutionExp}_N\}$ \\ \textit{ 
   s.t.   }\text{Everyone gets electricity and nothing breaks,} \\
    $\text{      }\sum \text{Costs} \leq C^*+Threshold$ }};

\node (result) [stop, below of=obj2] {\shortstack[l]{Outputs\\• Time-varying generation for each resource \\ • New Generation Capacity \\ • New Transmission Capacity}};

@@

\begin{frame}{Our Approach}
    \begin{enumerate}
        \item Use EPA emissions data to calculate emissions rates (Pounds per MWh)
        \item Use InMap Source-Receptor Matrix to calculate how one MWh of generation for each resource affects population-weighted average exposure for different groups.
        \item Use Switch to calculate least cost planning costs.
        \item Modify and run Switch to minimize air pollution exposure subject to a cost constraint.
    \end{enumerate}

@@

@@

    Please feel free to contact me at:
    \href{mailto:lbeatty@edf.org}{lbeatty@edf.org}\\
    \vspace{1cm}
\end{frame}

\begin{frame}{Bonus Slide!}
    This project started as a side-project to the Model Intercomparison Project -- a project aimed at harmonizing the inputs and comparing multiple open-source electricity planning models.

    \vspace{.4cm}

    \includegraphics[width=0.3\textwidth]{Figures/Output/ISRM_deathrate_by_scenario_2030.jpg}
    \includegraphics[width=0.3\textwidth]{Figures/Output/ISRM_deathrate_by_scenario_2040.jpg}
    \includegraphics[width=0.3\textwidth]{Figures/Output/ISRM_deathrate_by_scenario_2050.jpg}

\begin{itemize}
    \item Death rates vary widely across racial groups.
    \item Aggressive carbon policies reduce pollution exposure the fastest.
    \item Optimistic -- even under current policies future generations should have much better air quality.
\end{itemize}
